% LOCKED SCAFFOLD - Volume I FINAL TOC - Chapter 1 only
% Do not add Ch 2+ content to this file
\chapter{Foundations of Angular Electromagnetic Structure}
\label{ch:01}

\section{Introduction and Scope}
\label{sec:ch01.0}

Chapter~\ref{ch:01} introduces the conceptual framework used throughout the
monograph. The aim at this stage is to place the central question in clear
mathematical and physical terms before proceeding to detailed operator and
spectral developments. Section~\ref{sec:ch01.0.1} describes the scope and role of
the chapter, Section~\ref{sec:ch01.0.2} presents angular structure as a consequence
of Maxwell dynamics under symmetry and boundary conditions, and
Section~\ref{sec:ch01.0.3} specifies the admissibility class and validity domain
for the results that follow. This sequence provides a coherent foundation for
reading the subsequent derivations with appropriate assumptions and
interpretation.


\subsection{Scope and role of Chapter 1}
\label{sec:ch01.0.1}
% TOC tag: [HOME]

This monograph is written for advanced graduate students, doctoral researchers,
and practicing scientists or engineers who already command Maxwell theory and
vector analysis, and who require a proof-structured treatment of angular
electromagnetic organization \cite{jackson1999,harrington2001,collin2001}. The
chapter mandate is not to compile device narratives; it is to establish the
physical and mathematical language under which later statements are judged
admissible, realizable, and observable.

Chapter~\ref{ch:01} has a precise foundational function within Volume~I. It
establishes, in one place, the statements that subsequent chapters will invoke
without re-derivation: Maxwellian field structure in the adopted phasor
convention and SI system, conservation relations for energy and momentum
transport, and the distinction between representational descriptors and
operational observables. The chapter is therefore not an orientation survey; it
is the formal base from which later operator and spectral developments are read.

The assumptions adopted here are classical and explicit. The analysis remains
within Maxwell electrodynamics with admissible sources, admissible boundary
data, and the time convention \(\exp(-\jj\omega t)\). The intended reader is
expected to possess graduate-level preparation, yet the exposition remains
derivationally complete at each theorem-bearing step so that inferential
continuity is preserved and technical conclusions are traceable to stated
premises.

Its scope boundary is equally deliberate. This chapter does not construct the
full operator-domain program developed in Chapter~2, the eigenfield
representation machinery developed in Chapter~3, or the finite-geometry
realizability limits developed in Chapter~4. Those subjects are treated at
their designated proof homes and then inherited forward by reference, in
accordance with the forward progression architecture of the manuscript.

Within these limits, the chapter clarifies the working meaning of angular
electromagnetic structure: directional organization, rotational covariance, and
angular-momentum content are interpreted through conservation-governed field
quantities and measurement procedures, rather than through nomenclature based on
phase pattern alone.

This scope statement leads directly to Section~\ref{sec:ch01.0.2}, where the
origin of angular structure is developed from Maxwell symmetry and boundary
constraints.


\subsection{Angular structure from Maxwell symmetry and boundary conditions}
\label{sec:ch01.0.2}
% TOC tag: [HOME]

Angular structure is introduced here through Maxwell boundary-value dynamics
rather than through an a priori catalogue of modal labels
\cite{jackson1999,harrington2001}. Let \(\Omega\subset\mathbb{R}^3\) denote the
analysis region, \(\Gamma=\partial\Omega\) its boundary, \(\chi\) the
constitutive descriptor of the medium model, and \(\Jimp\) the impressed
electric current density. Under these declarations, the phasor fields are
written as
\begin{equation}
\label{eq:ch1.maxwell-map}
(\E,\H)=\mathcal{M}_{\Omega,\Gamma,\chi}\!\left[\Jimp\right],
\end{equation}
where \(\mathcal{M}_{\Omega,\Gamma,\chi}\) denotes the Maxwell map from
admissible source data to admissible field pairs. Equation
\eqref{eq:ch1.maxwell-map} assigns angular organization to the image structure
of a constrained operator, not to coordinate naming conventions. Physically,
Eq.~\eqref{eq:ch1.maxwell-map} places angular behavior within the same causal
framework that governs electromagnetic transport and exchange
\cite{jackson1999,collin2001}.

To separate transport observables from representation coordinates, define
\begin{equation}
\label{eq:ch1.angular-observable-map}
\mathcal{A}(\E,\H)=\big(\rho_J,\Phi_J,\Sigma\big),
\end{equation}
where \(\rho_J\) denotes an angular-momentum density observable, \(\Phi_J\)
denotes angular-momentum flux across a specified surface, and \(\Sigma\) denotes
chosen angular representation coefficients. Equation
\eqref{eq:ch1.angular-observable-map} distinguishes three non-equivalent levels
of description: local storage through \(\rho_J\), transported content through
\(\Phi_J\), and representational decomposition through \(\Sigma\). The
operational interpretation follows directly from
Eq.~\eqref{eq:ch1.angular-observable-map}: phase structure alone is not taken as
evidence of transported angular momentum unless flux and conservation accounting
support that conclusion \cite{jackson1999,harrington2001}.

The symmetry consequence can now be stated in compact form. When the effective
Maxwell map commutes with active rotational action, rotationally adapted field
structure is preserved; when this commutation is broken by geometry,
constitutive anisotropy, or boundary restriction, angular coupling and spectral
redistribution appear as structural consequences \cite{harrington2001,collin2001}.
In Chapter~\ref{ch:01}, this result is established at principle level; rigorous
operator proofs and representation-level elaboration are deferred to their HOME
developments in later chapters.


\subsection{Assumptions, finite-energy admissibility, and domain of validity}
\label{sec:ch01.0.3}
% TOC tag: [HOME]

The present chapter is formulated on an admissible finite-energy field class.
For the declared analysis region \(\Omega\subset\mathbb{R}^3\), the working
condition is
\begin{equation}
\label{eq:ch1.energy-class}
\int_{\Omega}\!\left(\E^*\!\cdot\E+\H^*\!\cdot\H\right)\,dV<\infty,
\end{equation}
where \((\cdot)^*\) denotes complex conjugation, and \(dV\) is the volume
element on \(\Omega\). Equation~\eqref{eq:ch1.energy-class} identifies the
function class in which field inner products, norm-based estimates, and later
projection arguments are mathematically well-posed. At the level of physical
interpretation, Eq.~\eqref{eq:ch1.energy-class} excludes infinite-energy
idealizations from the admissible state space and thereby enforces realizable
electromagnetic modeling \cite{jackson1999,collin2001}.

The accompanying assumptions are fixed throughout Chapter~\ref{ch:01}: SI unit
normalization, phasor convention \(\exp(-\jj\omega t)\) with \(\omega>0\), and
linear local constitutive closure unless an explicit exception is introduced in
a later HOME section. Every symbol is defined at first appearance and used in
the notation regime locked for Volume~I.

The validity boundary is therefore explicit and non-ambiguous. Strongly
nonlinear response, active gain media, rapidly time-varying constitutive laws,
and quantum-field corrections are outside the theorem scope of this chapter.
Such regimes are referenced only where their formal treatment is assigned in the
forward map \cite{harrington2001,jackson1999}. This admissibility statement
completes Subsection~\ref{sec:ch01.0.3} and provides the closure required for the
Section~\ref{sec:ch01.0} bridge that follows.

\paragraph{Section 1.0 summary and bridge.}
Section~\ref{sec:ch01.0} has now fixed the scope, clarified the physical origin
of angular structure, and declared the admissibility regime under which
subsequent claims are meaningful. With this framework in place, the chapter
proceeds to Section~\ref{sec:ch01.1}, where Maxwell equations and conservation
laws are developed as the first formal backbone of the monograph.


\section{Maxwell Theory and Conservation Laws}
\label{sec:ch01.1}

Section~\ref{sec:ch01.1} establishes the governing dynamical core that all later
angular claims must inherit: Maxwell equations in the adopted SI phasor
convention, admissible source and boundary data, well-posed evolution, and the
continuity laws that connect local field structure to measurable transfer of
energy, linear momentum, and angular momentum. The subsection sequence is
organized so that conservation statements are read as consequences of the same
field equations, not as independent postulates.


\subsection{Maxwell equations: differential, integral, vacuum constitutive relations}
\label{sec:ch01.1.1}
% TOC tag: [HOME]


\subsection{Sources, boundary conditions, and physical admissibility}
\label{sec:ch01.1.2}
% TOC tag: [HOME]


\subsection{Initial-boundary value problems and uniqueness}
\label{sec:ch01.1.3}
% TOC tag: [HOME]


\subsection{Energy, linear momentum, and Maxwell stress tensor}
\label{sec:ch01.1.4}
% TOC tag: [HOME]


\subsection{Angular momentum conservation and torque balance}
\label{sec:ch01.1.5}
% TOC tag: [HOME]

\paragraph{Section 1.1 summary and transition.}
With the Maxwell-conservation backbone fixed in
Section~\ref{sec:ch01.1}, the chapter can define angular structure without
ambiguity about what is physically transported and what is merely representational.
The discussion therefore advances to Section~\ref{sec:ch01.2}, where angular
organization is formulated directly in field-theoretic terms.


\section{Angular Structure of Electromagnetic Fields}
\label{sec:ch01.2}

Section~\ref{sec:ch01.2} develops the meaning of angular structure from
field quantities and transport criteria rather than from phase-pattern naming.
Its scope is to separate directional geometry, polarization-phase organization,
and genuine angular-momentum carriage under explicit radiative and reactive
regimes, so that each later modal interpretation remains tied to an operational
electromagnetic criterion.


\subsection{Directional dependence and angular momentum}
\label{sec:ch01.2.1}
% TOC tag: [HOME]


\subsection{Amplitude, phase, polarization, and Poynting topology}
\label{sec:ch01.2.2}
% TOC tag: [HOME]


\subsection{Conditions for angular-momentum transport}
\label{sec:ch01.2.3}
% TOC tag: [HOME]


\subsection{Reactive and radiative regimes}
\label{sec:ch01.2.4}
% TOC tag: [HOME]

\paragraph{Section 1.2 synthesis and bridge.}
Section~\ref{sec:ch01.2} identifies the conditions under which angular features
correspond to transport-capable electromagnetic content. This clarification
prepares the covariance analysis in Section~\ref{sec:ch01.3}, where rotational
actions and tensor structure are treated explicitly.


\section{Rotations, Tensors, and Covariance}
\label{sec:ch01.3}

Section~\ref{sec:ch01.3} places angular discourse in the language of coordinate
transformations and invariant statements. The objective is to ensure that claims
about angular behavior remain physically interpretable under frame changes,
origin shifts, and tensorial reformulation, thereby preventing coordinate
artifacts from entering theorem-level conclusions.


\subsection{Active and passive rotations}
\label{sec:ch01.3.1}
% TOC tag: [HOME]


\subsection{Transformation of vectors, tensors, and dyads}
\label{sec:ch01.3.2}
% TOC tag: [HOME]


\subsection{Origin dependence and translational covariance}
\label{sec:ch01.3.3}
% TOC tag: [HOME]


\subsection{Invariants and frame-independent observables}
\label{sec:ch01.3.4}
% TOC tag: [HOME]

\paragraph{Section 1.3 closure and forward link.}
After Section~\ref{sec:ch01.3}, rotational covariance and frame-invariant
interpretation are established as mandatory constraints on admissible angular
claims. The chapter next addresses gauge structure in
Section~\ref{sec:ch01.4}, where representational freedom and physical
observables are separated with explicit care.


\section{Gauge Structure and Physical Observables}
\label{sec:ch01.4}

Section~\ref{sec:ch01.4} treats potentials, gauge transformations, and helicity
with emphasis on what survives as an observable quantity. The section is
constructed to prevent local decomposition language from being misread as
gauge-independent physics; every assertion is filtered through an explicit
observability criterion before it is carried forward.


\subsection{Potentials and gauge transformations}
\label{sec:ch01.4.1}
% TOC tag: [HOME]


\subsection{Gauge dependence of local densities}
\label{sec:ch01.4.2}
% TOC tag: [HOME]


\subsection{Gauge-invariant observables, helicity, and dual symmetry}
\label{sec:ch01.4.3}
% TOC tag: [HOME]


\subsection{Operational definitions of observables}
\label{sec:ch01.4.4}
% TOC tag: [HOME]


\subsection{Limits of local spin-orbit decompositions}
\label{sec:ch01.4.5}
% TOC tag: [HOME]

\paragraph{Section 1.4 summary and continuation.}
Section~\ref{sec:ch01.4} delineates the boundary between gauge-dependent
descriptors and gauge-robust observables. On that basis, the chapter proceeds to
Section~\ref{sec:ch01.5}, where measurement channels and interpretation limits
are formalized without reintroducing gauge ambiguity.


\section{Measurement and Interpretation}
\label{sec:ch01.5}

Section~\ref{sec:ch01.5} translates formal field statements into experimentally
resolvable quantities. Its purpose is to define how torque, flux, and modal
projections are interpreted under finite apparatus and finite information, while
maintaining strict separation between direct observables and inferred
reconstructions.


\subsection{Field-matter interaction}
\label{sec:ch01.5.1}
% TOC tag: [HOME]


\subsection{Torque, momentum flux, and stress measurements}
\label{sec:ch01.5.2}
% TOC tag: [USE SS1.1.4]


\subsection{Modal projections and measurement limits}
\label{sec:ch01.5.3}
% TOC tag: [HOME]


\subsection{Observables versus inferred quantities}
\label{sec:ch01.5.4}
% TOC tag: [HOME]

\paragraph{Section 1.5 consolidation and handoff.}
The measurement framework in Section~\ref{sec:ch01.5} supplies the operational
tests that later examples must satisfy. Section~\ref{sec:ch01.6} therefore uses
worked problems and counterexamples to demonstrate where conservation-consistent
interpretation is sustained and where phase-only inference fails.


\section{Examples and Counterexamples}
\label{sec:ch01.6}
% TOC tag: [FIG+PROB]

Section~\ref{sec:ch01.6} is the verification layer of Chapter~\ref{ch:01}. Each
subsection is drafted in full problem form, with schematic support and explicit
mathematical steps, to test the theoretical criteria established earlier against
canonical and limiting cases.


\subsection{Angular momentum conservation in radiation}
\label{sec:ch01.6.1}
% TOC tag: [FIG+PROB][USE SS1.1.5]


\subsection{Phase structure without angular-momentum transport}
\label{sec:ch01.6.2}
% TOC tag: [FIG+PROB][HOME]


\subsection{Gauge dependence of local angular-momentum densities}
\label{sec:ch01.6.3}
% TOC tag: [FIG+PROB][USE SS1.4.2]


\subsection{Reactive versus radiative comparison}
\label{sec:ch01.6.4}
% TOC tag: [FIG+PROB][USE SS1.2.4]

\paragraph{Section 1.6 outcome and bridge.}
These worked cases delimit the practical scope of angular claims by enforcing
conservation, covariance, and gauge-discipline simultaneously. The chapter can
therefore conclude with Section~\ref{sec:ch01.7}, where established results are
separated from deferred developments under strict forward-only ownership.


\section{Chapter Summary and Forward Map}
\label{sec:ch01.7}

Section~\ref{sec:ch01.7} records the chapter's established outcomes, lists only
those concepts formally deferred to later HOME locations, and defines the exact
inheritance boundary into Chapter~2. No new theorem content is introduced here;
the function of this section is architectural closure of Chapter~\ref{ch:01}.


\subsection{Results established in Chapter 1}
\label{sec:ch01.7.1}
% TOC tag: [DEFER]


\subsection{Concepts deferred to Chapters 2-4 and Volume II}
\label{sec:ch01.7.2}
% TOC tag: [DEFER]


\subsection{Bridge to Chapter 2}
\label{sec:ch01.7.3}
% TOC tag: [DEFER]

\paragraph{Section 1.7 terminal summary.}
Chapter~\ref{ch:01} now stands as the sole HOME foundation for the core
Maxwell-conservation-gauge-observability structure used by subsequent chapters.
Chapter~2 inherits this base by reference and develops operator-domain and
radiation-mapping machinery without recursive re-derivation.


\bibliographystyle{IEEEtran}
\bibliography{references}

